G2GML: Graph to Graph Mapping Language for Bridging RDF and Property Graphs

### 2020-08-15 paper.tex

Recently, the property graph (PG) model~\cite{angles1,angles2} has been increasingly attracting attention in the context of graph analysis. Various graph database engines, including Neo4j~\cite{neo4j}, Oracle Database~\cite{oracle}, and Amazon Neptune~\cite{neptune} adopt this model. These graph database engines support algorithms for traversing or analyzing graphs. However, few datasets are published in the PG model and the lack of an ecosystem for exchanging data in the PG model limits the application of these powerful engines.

@@

The PG format has the following characteristics. An example is given in Figure~\ref{fig:example-pg}.

@@

\begin{defi}[EBNF notation of the PG format]
\leavevmode
\begin{verbatim}
 pg         ::= (node | edge)+
 node       ::= NODE_ID labels properties NEWLINE
 edge       ::= NODE_ID direction NODE_ID labels properties NEWLINE
 labels     ::= label*
 properties ::= property*
 label      ::= ":" STRING
 property   ::= STRING ":" value
 value      ::= STRING | NUMBER
 direction  ::= "--" | "->"
\end{verbatim}
\end{defi}

@@

\begin{figure}
\center
\includegraphics[width=0.5\textwidth]{pg_example5.png}
\caption{Example of output PG data}
\label{fig:pg_example5}
\end{figure}

@@

@@

>>>>

Recently, the property graph (PG) model~\cite{angles1,angles2} has been increasingly attracting attention in the context of graph analysis~\cite{agri}. Various graph database engines, including Neo4j~\cite{neo4j}, Oracle Database~\cite{oracle}, and Amazon Neptune~\cite{neptune} adopt this model. These graph database engines support algorithms for traversing or analyzing graphs. However, few datasets are published in the PG model and the lack of an ecosystem for exchanging data in the PG model limits the application of these powerful engines.

@@

The PG format has the following characteristics. An example is given in Figure~\ref{fig:example-pg}, which is visualized in Figure~\ref{fig:pg_example5}.

@@

\begin{defi}[EBNF notation of the PG format]
\leavevmode
\begin{verbatim}
 pg         ::= (node | edge)+
 node       ::= NODE_ID labels properties NEWLINE
 edge       ::= NODE_ID direction NODE_ID labels properties NEWLINE
 labels     ::= label*
 properties ::= property*
 label      ::= ":" STRING
 property   ::= STRING ":" VALUE
 direction  ::= "--" | "->"
\end{verbatim}
\end{defi}

According to this definition, each property value of PGs is a set of items of any datatype. Meanwhile, our G2G mapping prototype implementation currently supports the main three datatypes (integer, double, and string) as property value, and those types are inferred from the serialized values.

@@

\begin{figure}
\center
\includegraphics[width=0.5\textwidth]{pg_example5.png}
\caption{Visualization of Figure 5}
\label{fig:pg_example5}
\end{figure}

@@

For the future adoption of this framework, we expect two scenarios: The use of the standalone G2G mapping tools, such as our implementation, for generating PG datasets from RDF resources. Also, the adoption of the framework within the database management systems which support both RDF and PG datasets.

@@

\bibitem{agri}
Abad-Navarro, F., Bernabé-Diaz, J. A., García-Castro, A., & Fernandez-Breis, J. T. (2020). Semantic Publication of Agricultural Scientific Literature Using Property Graphs. Applied Sciences, 10(3), 861.
